### 2011-08-02 doc/theses/svirec/kap6.tex
fixing experiments

The first real-world data (course data) is represented by \texttt{reed.xml} and \texttt{wsu.xml}. For each document, we execute our algorithm with three different settings. First two use the default value of $k$ ($k=1.5$), for the last one, we set $k=0.005$. For the second (third) execution, we set the weight $w$ of nodes represented by XPath \texttt{/root/course/time/start\_time/text()} (resp. \texttt{/root/course/time/\discretionary{}{}{}start/text()}) to 0.1.

@@

Setting the weight to particular nodes effects the choise of strategies used to repair the violations. In datasets \texttt{reed.xml} and \texttt{wsu.xml} setting the custom weight to nodes causes the node values are changed to values of other nodes. On the other side, in datasets \texttt{actors.xml} and \texttt{customers.xml} setting the weights causes changing the value of nodes to a newly generated one.

>>>>

The first real-world data (course data) is represented by \texttt{reed.xml} and \texttt{wsu.xml}. For each document, we execute our algorithm with three different settings. First two use the default value of $k$ ($k=1.5$), for the last one, we set $k=0.005$. For the last two executions, we set for \texttt{reed.xml} (\texttt{wsu.xml}) the weight $w$ of nodes represented by XPath \texttt{/root/course/time/start\_time/text()} (resp. \texttt{/root/\discretionary{}{}{}course/time/\discretionary{}{}{}start/text()}) to 0.1.

@@

Setting the weight to particular nodes causes two different behaviour of the algorithm. First, setting the weights effects the choise of strategies used to repair the violations. In datasets \texttt{actors.xml} and \texttt{customers.xml} setting the custom weight to nodes causes the node values are changed to values of other nodes. Second causes modification of nodes defined by the path specifying the weights. In datasets \texttt{reed.xml} and \texttt{wsu.xml} setting the weights still changes the value of nodes to a newly generated one, however for \texttt{reed.xml} only values of nodes defined by \texttt{/root/course/time/start\_time/\discretionary{}{}{}text()} are modified and for \texttt{wsu.xml} are modified values defined by \texttt{root/\discretionary{}{}{}course/time/start/text()}.
